---
title: "DATA605_HW4_ChunjieNan"
author: "Chunjie Nan"
date: "2/19/2022"
output: html_document
---


### With the attached data file, build and visualize  eigenimagery that accounts for 80% of the variability.  Provide full R code and discussion.



### Import Libraries
```{r}
library(doParallel)
library(foreach)
library(jpeg)
library(OpenImageR)
library(BiocManager) 
library(EBImage)

```

There are 17 shoes images in the jpg folder.
```{r}

files=list.files("/Users/chunjienan/Desktop/DATA605 Fundamentals of computational mathmatics/week4/jpg",pattern="\\.jpg")[1:17] 
```


### Set shoes image function

```{r}
height=1200; width=2500;scale=20
plot_jpeg = function(path, add=FALSE)
{ jpg = readJPEG(path, native=T) 
  res = dim(jpg)[2:1] 
  if (!add) 
    plot(1,1,xlim=c(1,res[1]),ylim=c(1,res[2]),asp=1,type='n',xaxs='i',yaxs='i',xaxt='n',yaxt='n',xlab='',ylab='',bty='n')
  rasterImage(jpg,1,1,res[1],res[2])
}
```


### Load the data, resize and scale the images.

```{r}
images=array(rep(0,length(files)*height/scale*width/scale*3), dim=c(length(files), height/scale, width/scale,3))

for (i in 1:17){
  temp=resize(readJPEG(paste0("/Users/chunjienan/Desktop/DATA605 Fundamentals of computational mathmatics/week4/jpg/", files[i])),height/scale, width/scale)
  images[i,,,]=array(temp,dim=c(1, height/scale, width/scale,3))}

```


### Vectorize 

```{r}
mat=matrix(0, 17, prod(dim(images))) 
for (i in 1:17) {
  imp <- readJPEG(paste0("/Users/chunjienan/Desktop/DATA605 Fundamentals of computational mathmatics/week4/jpg/", files[i]))
  r=as.vector(images[i,,,1]); g=as.vector(images[i,,,2]);b=as.vector(images[i,,,3])
  mat[i,] <- t(c(r, g, b))
}
shoes=as.data.frame(t(mat))


```


### Plot the shoes
```{r}

par(mfrow=c(3,4))
par(mai=c(.3,.3,.3,.3))
for (i in 1:17){ 
plot_jpeg(writeJPEG(images[i,,,]))
}
```


### Structure of Eigencomponents

```{r}
scaled=scale(shoes, center = TRUE, scale = TRUE)
mean.shoe=attr(scaled, "scaled:center") 
std.shoe=attr(scaled, "scaled:scale") 
dim(scaled)
str(scaled)
```

### Correlation Matrix for eigencomponents.
```{r}
Sigma_=cor(scaled)
dim(Sigma_)
str(Sigma_)
```

### Eigencomponents 
```{r}
myeigen=eigen(Sigma_)
cumsum(myeigen$values) / sum(myeigen$values)

```

### Findout Engenshoes

The 80% variability is at 2nd position

```{r}
scaling=diag(myeigen$values[1:2]^(-1/2)) / (sqrt(nrow(scaled)-1))
eigenshoes=scaled%*%myeigen$vectors[,1:2]%*%scaling
imageShow(array(eigenshoes[,2], c(60,125,3)))

```
