---
title: "DATA605_HW1_ChunjieNan"
author: "Chunjie Nan"
date: "1/30/2022"
output:
  html_document: default
  pdf_document: default
---

One of the most useful applications for linear algebra in data science is image manipulation.  We often need to compress, expand, warp, skew, etc. images.  To do so, we left multiply a transformation matrix by each of the point vectors.  

For this assignment, build the first letters for both your first and last name using point plots in R.  For example, the following code builds an H.

x=c(rep(0,500),seq(0,1,length.out=1000), rep(1,500))

y=c(seq(-1,1,length.out=500),rep(0,1000), seq(-1,1,length.out=500))

z=rbind(x,y)

plot(y~x, xlim=c(-3,3), ylim=c(-3,3))

Then, write R code that will left multiply (%>%) a square matrix (x) against each of the vectors of points (y). Initially, that square matrix will be the Identity matrix.  

Use a loop that changes the transformation matrix incrementally to demonstrate 1) shear, 2) scaling, 3)  rotation , and 4) projection in animated fashion.  


```{r}
library(dplyr)
library(plotly)
library(gifski)
library(anim.plots)
```


My name is Chunjie Nan, therefore, the letters that I would like to plot is "CN". 

```{r}
x=c(rep(0,100), cos(seq(pi,pi*0.15,length.out=2000)/2), seq(1,1,length.out=100), sin(seq(pi*0.01,pi*-1,length.out=2000))/1.6-0.5)
y=c(seq(-0.8,0.8,length.out=100),seq(1,-1,length.out=2000),seq(1,-1,length.out=100), seq(-0.8,1,length.out=2000))

binded=rbind(x,y)
plot(y~x, xlim=c(-3,3), ylim=c(-3,3), col='Blue')
```


## leftMultiply function

```{r}
leftMultiply  <- function(x,y){
   x %*% y
}
leftMultiply(matrix(rep(seq(1,3, length.out=3),3), nrow = 3, ncol = 3),diag(3))

```

## Shearing movement

```{r}

for (i in seq(0,1,length.out=20)) {
  z<-apply(binded,2,function(x) leftMultiply(x,matrix(c(1,i,0,1),nrow=2,ncol=2)))
 # plot(z[2,]~z[1,], xlim=c(-3,3), ylim=c(-3,3), col='Blue')

}


img_sh <- list("000003.png", "000004.png", "000005.png",
            "000006.png", "000007.png", "000008.png", 
            "000009.png","000010.png","000011.png","000012.png","000013.png","000014.png","000015.png","000017.png","00000a.png","00000b.png","00000c.png","00000d.png","00000e.png","00000f.png")

list_sh <- lapply(img_sh, magick::image_read)

# join the images together
sh_joined <- magick::image_join(list_sh)

# animate at 1 frames per second
sh_animated <- magick::image_animate(sh_joined, fps = 1)

# view animated image
sh_animated

```







## Scaling

```{r}
for (i in seq(1,4,length.out=20)) {
  z<-apply(binded,2,function(x) leftMultiply(x,matrix(c(i,0,0,i),nrow=2,ncol=2)))
   #plot(z[2,]~z[1,], xlim=c(-3,3), ylim=c(-3,3), col='Blue')
}

img_sc <- list("2.png", "3.png", "4.png",
            "5.png", "6.png", "7.png", 
            "8.png","9.png","10.png","11.png","12.png","13.png","14.png","15.png","16.png","17.png","18.png","19.png","20.png","21.png")

list_sc <- lapply(img_sc, magick::image_read)

# join the images together
sc_joined <- magick::image_join(list_sc)

# animate at 1 frames per second
sc_animated <- magick::image_animate(sc_joined, fps = 1)

# view animated image
sc_animated
```



## Rotation

```{r}
for (i in seq(0,pi*4,length.out=20)) {
  z<-apply(binded,2,function(x) leftMultiply(x,matrix(c(cos(i),-sin(i),sin(i),cos(i)),nrow=2,ncol=2)))
   #plot(z[2,]~z[1,], xlim=c(-3,3), ylim=c(-3,3), col='Blue')
}


img_r <- list("22.png", "23.png", "24.png",
            "25.png", "26.png", "27.png", 
            "28.png","29.png","30.png","31.png","32.png","33.png","34.png","35.png","36.png","37.png","38.png","39.png","40.png","41.png")

list_r <- lapply(img_r, magick::image_read)

# join the images together
r_joined <- magick::image_join(list_r)

# animate at 1 frames per second
r_animated <- magick::image_animate(r_joined, fps = 1)

# view animated image
r_animated

```



## Projection

```{r}
for (i in seq(0,pi*4,length.out=20)) {
  t<-rbind(binded,rep(0,ncol(binded)))
  z<-apply(t,2,function(x) leftMultiply(x,matrix(c(1,0,0,0,cos(i),-sin(i),0,sin(i),cos(i)),nrow=3,ncol=3)))
   #plot(z[2,]~z[1,], xlim=c(-3,3), ylim=c(-3,3), col='Blue')
}


img_p <- list("42.png", "43.png", "44.png",
            "45.png", "46.png", "47.png", 
            "48.png","49.png","50.png","51.png","52.png","53.png","54.png","55.png","56.png","57.png","58.png","59.png","60.png","61.png")

list_p <- lapply(img_p, magick::image_read)

# join the images together
p_joined <- magick::image_join(list_p)

# animate at 1 frames per second
p_animated <- magick::image_animate(p_joined, fps = 1)

# view animated image
p_animated
```